{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-07 thesis/landslide.tex
fix some figure placements, footnote stuffs, cref stuffs

Use of {\tt tell\_landslide()} annotations
\revisionminor{(\cref{sec:tell-landslide})}
is not necessary,
although {\tt tell\_landslide\_\allowbreak{}preempt()} and {\tt tell\_landslide\_dump\_stack()}
may optionally be used at the user's convenience.
Additionally, the following ``secret'' annotations
are occasionally used in the pre-supplied test cases
to accomplish several mysterious goals described hereupon.

@@

Ultimately, the second half of the state space is pruned symmetrically.
In general, the number of ways to interleave two threads executing $N$ and $M$ events each is given by ${N+M \choose N}$%
\footnote{Generalizing to $K$ threads, and simplifying to $N$ events each,
this formula becomes $\frac{n!k!}{n!^k}$.};
in this case, the original state space's size was ${3+3 \choose 3} = 20$.
DPOR's reduction is characterized by replacing $N$ and $M$ with the number of {\em conflicting} events only;
in this case, ignoring all {\tt tmpN++} reorderings and testing only ${2+2 \choose 2} = 6$ branches.

@@

Implementation-wise, Landslide reports size estimates as both the percentage and as a total number of branches,
and time estimates as an ETA.
Quicksand's {\tt -v} option (\cref{sec:landslide-quicksand-options})
will cause it to print them each time a new interleaving is tested; for example:
\begin{center}
	{\tt \small [JOB 1] progress: 66101/94825 brs (69.708252\%), ETA 13m 37s (elapsed 46m 10s)}
\end{center}
Both estimates are computed simultaneously in {\tt \_estimate()} in {\tt estimate.c}
(which, I might add, is well-commented in case the following prose is insufficient).
%I summarize their respective implementations here.
\Cref{chap:warpzone-heuristics} will discuss their limitations and some opportunities for future improvement.

@@

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=0.28\textwidth]{heuristic-livelock.pdf}
			&
			\includegraphics[width=0.28\textwidth]{heuristic-tightloop.pdf}
			\\
			(a) Infinite loop around preemption points.
			&
			(b) Stuck between preemption points.
		\end{tabular}
	\end{center}
	\caption{Detecting infinite loops heuristically by comparison to past interleavings.}
	\label{fig:heuristic-loop}
\end{figure}

@@

>>>>

Use of the {\tt tell\_landslide()} annotations
\revisionminor{(\cref{sec:tell-landslide})}
is not necessary,
although {\tt tell\_\allowbreak{}landslide\_preempt()} and {\tt tell\_landslide\_dump\_stack()}
may optionally be used at the user's convenience.
Additionally, the following ``secret'' annotations
are occasionally used in the pre-supplied test cases
to accomplish several mysterious goals described hereupon.

@@

Ultimately, the second half of the state space is pruned symmetrically.
In general, the number of ways to interleave two threads executing $N$ and $M$ events each is given by ${N+M \choose N}$;%
\footnote{Generalizing to $K$ threads, and simplifying to $N$ events each,
this formula becomes $\frac{n!k!}{n!^k}$.}
in this case, the original state space's size was ${3+3 \choose 3} = 20$.
DPOR's reduction is characterized by replacing $N$ and $M$ with the number of {\em conflicting} events only;
in this case, ignoring all {\tt tmpN++} reorderings and testing only ${2+2 \choose 2} = 6$ branches.

@@

Implementation-wise, Landslide reports size estimates as both the percentage and as a total number of branches,
and time estimates as an ETA.
Quicksand's {\tt -v} option (\cref{sec:landslide-quicksand-options})
will cause it to print them each time a new interleaving is tested; for example:
\begin{center}
	{\tt \small [JOB 1] progress: 66101/94825 brs (69.708252\%), ETA 13m 37s (elapsed 46m 10s)}
\end{center}
Both estimates are computed simultaneously in {\tt \_estimate()} in {\tt estimate.c}
(which, I might add, is well-commented in case the following prose is insufficient).
%I summarize their respective implementations here.
\cref{sec:warpzone-heuristics} will discuss their limitations and some opportunities for future improvement.

@@

@@

\begin{figure}[t]
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=0.28\textwidth]{heuristic-livelock.pdf}
			&
			\includegraphics[width=0.28\textwidth]{heuristic-tightloop.pdf}
			\\
			(a) Infinite loop around preemption points.
			&
			(b) Stuck between preemption points.
		\end{tabular}
	\end{center}
	\caption{Detecting infinite loops heuristically by comparison to past interleavings.}
	\label{fig:heuristic-loop}
\end{figure}
